Conditional selectivity for triplestores

### 2012-09-17 conditional/trunk/selectivity-basic.tex
Subject unbound, object and predicate bound
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@374 43ef1190-90fd-4dd7-a769-d0121f02b80e

From Eq.~\ref{eq:sel} directly. We again note that
since the the unbound subject will always have selectivity of
unity.
Eq.~\ref{eq:sel} thus reduces to:

% \begin{equation}\label{eq:selsubjun}
% \sel{T_{\{?~p~o\}}) = \sel{O | P) \cdot \sel{P) . 
% \end{equation}

% Since property partitions detail statistics given a certain predicate,
% they can be used in the conditional case. We can therefore write:

% \begin{equation}\label{eq:selsubjunp}
% \sel{P = p) = \frac{\rdfterm{void:propertyPartition/void:triples}}{|d|}
% \end{equation}
% and
% \begin{equation}\label{eq:selsubjunop}
% \sel{O = o|P = p) =
% \frac{\rdfterm{void:propertyPartition/void:distinctObjects}}{\rdfterm{void:propertyPartition/void:triples}} .
% \end{equation}
% Thus,
% \begin{equation}\label{eq:selsubjunres}
% \sel{T_{\{?~p~o\}}) =
% \frac{\rdfterm{void:propertyPartition/void:distinctObjects}}{|d|} ,
% \end{equation}\todo{WRONG!}
% where the notation is inspired by SPARQL 1.1 Property Paths,
% for example the relevant part of a VoID description for the second
% example in section~\ref{sec:example} would be:
% \begin{verbatim}
% </dataset> a void:Dataset ;
%            void:propertyPartition [
%                 void:property foaf:firstName;
%                 void:distinctObjects 2 .
%            ]
% \end{verbatim}

% there exists a \rdfterm{void:propertyPartition} predicate that
% has an object which is again linked to a dataset subset containing the
% property $p$ as predicate of

>>>>

This case is similar to the above, and we can write 
\begin{equation}\label{eq:selsuobunpb}
\sel{T_{\{?~p~?\}}} = \sel{O = ? | P = p \cap S = s} \cdot 
\sel{S = s | P = p} \cdot
\sel{P = p} . 
\end{equation}
We note that we can't find the first two parts in the VoID
description, but we also note with interest that the first part shows
that only the marginal distribution of objects is needed to estimate
this part.
